Peer Accessment 1 
====================================
###Loading and preprocessing the data
Seeting the local working directory to read the csv file.
```{r}
setwd('/Users/JohnnyChiu/Desktop/檔案總管/學習/coursera/JohnHopkins-DataScience/Reproducible research/project1/')
data<-read.csv('activity.csv')
head(data)
```


###What is mean total number of steps taken per day?
I will use the dplyr package to transform the data, and use ggplot2 to plot.

```{r}
library(dplyr)
library(ggplot2)
transform_data_1<-data %>% group_by(date) %>% summarize(sum=sum(steps))
dim(transform_data_1)  

mean<-mean(transform_data_1$sum,na.rm=TRUE)  
median<-median(transform_data_1$sum,na.rm=TRUE)  

qplot(sum,data=transform_data_1,fill=date)   #It's the histogram of it
qplot(date,sum,data=transform_data_1,geom="bar",stat="identity")   #It's the bar plot of it
```

  
*The mean and median of the total number of steps taken per day is **`r mean`** and **`r median`** *

###What is the average daily activity pattern?
1.  Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)

```{r}
transform_data_2<-data %>% group_by(interval) %>% summarize(mean=mean(steps,na.rm=TRUE))
qplot(interval,mean,data=transform_data_2,geom="line",stat="identity")
ggplot(transform_data_2, aes(interval, mean)) + geom_line()

transform_data_3<-transform_data_2 %>% filter(mean==max(transform_data_2$mean))
max_interval<-as.double(transform_data_3[1,1])
```
2.  Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?  
*The **`r max_interval`** 5-minute interval contains the maximum number of steps*

###Imputing missing values
1.  Calculate and report the total number of missing values in the dataset (i.e. the total number of rows with NAs)
```{r}
transform_data_4<-data %>% filter(is.na(steps))
na_row<-dim(transform_data_4)[1]
```
*The total number of missing values are **`r na_row`***

2.  Devise a strategy for filling in all of the missing values in the dataset. The strategy does not need to be sophisticated. For example, you could use the mean/median for that day, or the mean for that 5-minute interval, etc.

```{r}
transform_data_5<-data
for(i in 1:dim(transform_data_5)[1]){
  if(is.na(transform_data_5[i,1])){
    for(j in 1:dim(transform_data_2)[1]){
      if(transform_data_5[i,3]==transform_data_2[j,1]){
        transform_data_5[i,1]<-transform_data_2[j,2]
      }
    }
  }
}
transform_data_7<-data %>% group_by(date) %>% summarize(sum=sum(steps))
qplot(sum,data=transform_data_7,fill=date)
transformed_mean<-mean(transform_data_7$sum,na.rm=TRUE)  
transformed_median<-median(transform_data_7$sum,na.rm=TRUE)  
    
```

*The mean and median of the total number of steps taken per day after impute NA value is **`r transformed_mean`** and **`r transformed_median`** *

###Are there differences in activity patterns between weekdays and weekends?

```{r}
transform_data_8<-data
for(i in 1:dim(transform_data_8)[1]){
  transform_data_8$day[i]<-weekdays(as.Date(data[i,2]))
  if(transform_data_8$day[i]=='周日'|transform_data_8$day[i]=='周六'){
    transform_data_8$weekday[i]<-'weekend'
  }else{
    transform_data_8$weekday[i]<-'weekday'
  }
}

transform_data_8_weekday<-transform_data_8 %>% filter(weekday=='weekday') %>%
                          group_by(interval) %>% summarize(mean=mean(steps,na.rm=TRUE))
transform_data_8_weekend<-transform_data_8 %>% filter(weekday=='weekend') %>%
                          group_by(interval) %>% summarize(mean=mean(steps,na.rm=TRUE))
transform_data_8_weekday$weekday<-'weekday'
transform_data_8_weekend$weekday<-'weekend'
transform_data_9<-rbind(transform_data_8_weekday,transform_data_8_weekend)
qplot(interval,mean,data=transform_data_9,facets=weekday~.,geom="line")+ylab('number of steps')
```


